---
title: "Create a new Reference Standard"
author: "Glenn Sanders"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Create a new Reference Standard"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Create a new standard

To create a new standard the `pwr_corr` function is used.

The `ref_temp` and `ref_press` are self explanatory

The consideration of humidity may or may not be included. Humidty is used to adjust the wet pressure to an equivalent dry pressure. If `humidity = NA` then humidty is not taken into consideration in the calculations regardless of its input value. Friction is the same. If  `friction = NA` the no friction is included in the calculations.

As an example of the SAE J1349(2004) standard definition

```{r message=FALSE, warning=FALSE}
library(pwrcorr)
library(units)
j1349_2004 <- pwr_corr(ref_temp = set_units(77,"degF"),
                       ref_press = set_units(990,"hPa"),
                       humidity = 0,
                       friction = 0.85)
```

To use the equation then

```{r}
j1349_2004(set_units(65, "degF"),set_units(28.868, "inHg"),0.6)
```

